\section{Tomato and blood orange salad with ginger tahini sauce}
\emph{I first developed this recipe for a pop-up at the brilliant Supa Ya Ramen in London in late January. That week, blood oranges and iberiko winter tomatoes were glimmering on the shelves of my local grocer and I just knew I had to create something with them. What with the unpredictability of the seasons these days, I don’t know if blood oranges and iberiko tomatoes will still be singing quite as heartily whenyou read this, but you can always use regular oranges or tangerines instead of the blood oranges and any ripe, sweet tomato you can get your hands on.}\\\\ 
\textbf{Prep}: 15 min
\textbf{Cook}: 5 min
\textbf{Serves}: 4
\subsection*{Ingredients}
\begin{itemize}
\item 500g ripe winter tomatoes (I used iberiko tomatoes)
\item Salt
\item 3 blood oranges (or 2 regular oranges)
\item 3 spring onions, green ends julienned (save the rest for another dish)
\item Chiu chow or crispy chilli oil, to serve (optional)
\end{itemize}

\begin{itemize}
\item For the dressing
\item 4 tbsp light olive oil
\item 40g fresh ginger, peeled and julienned
\item 2 tbsp soy sauce or tamari 
\item 1 tbsp lime juice
\item 1 small garlic clove, finely grated/crushed
\item ½ tbsp maple syrup
\item ½ tsp toasted sesame oil
\end{itemize}

\begin{itemize}
\item For the tahini sauce
\item 60g tahini 
\item 2 tbsp maple syrup
\item 2 tbsp soy sauce
\item 1 tbsp lime juice
\item 1 tsp very finely grated fresh ginger
\end{itemize}

\subsection*{Steps}
\begin{enumerate}
\item For the dressing, put the oil and one stick of the ginger in a medium saucepan set over a medium-low heat. Once it starts to sizzle, add the rest of the ginger and fry gently, stirring often with a fork to separate the pieces, until the ginger is a light golden brown – this should take about three and a half minutes, but keep a close eye on it because the ginger can quite quickly turn from golden to brown and burnt. Strain the crisped ginger through a sieve, collecting the oil in a bowl underneath. Spread out the ginger on a plate, sprinkle with salt and set aside.
\item Put the soy sauce, lime juice, garlic, maple syrup and sesame oil in a large bowl with two tablespoons of the ginger frying oil. Cut the tomatoes into random, bite-sized pieces and add to the bowl. Add a pinch of salt, gently mix and set aside to marinate.
\item Put all the ingredients for the tahini ginger sauce in a medium bowl, add a tablespoon of water and whisk vigorously until completely smooth.
\item Cut the tops and bottoms off the oranges. Using a sharp knife, remove the skin and white pith, then cut between the individual membranes to release the segments. Add any juice to the tomato bowl and set aside the segments.
\item Spoon the tahini sauce on to a lipped platter. Top with the tomatoes, using your hands as a natural sieve so you don’t take all the dressing with you. Arrange the blood orange segments evenly among the tomatoes. Drizzle over some chilli oil, finish with the spring onions and crisp ginger, and serve with the remaining dressing on the side.
\item  Ixta Belfrage’s debut solo cookbook, Mezcla: Recipes to Excite, is published by Ebury in summer 2022. Meera Sodha is away.
\end{enumerate}
\newpage
